Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-06-24 paper/paper.Rmd
paper folder

---
  title: "Psych 254 Replication Project Analysis"
author: "Eric Smith, Robert Hawkins, Michael C. Frank"
date: '`r Sys.Date()`'
output:
  html_document:
  number_sections: yes
toc: yes
---

Assessing the Replicability of Psychological Science Through Pedagogy

@@

>>>>

---
title: "Assessing the Replicability of Psychological Science Through Pedagogy"
short-title: "Replication through pedagogy"
output: kmr::apa_manuscript
csl: apa6.csl
bibliography: replication254.bib

document-params: "a4paper,man,apacite,floatsintext"

bib-tex: "library.bib"

author-information:
    - \author{Eric Smith*}
    - \author{Robert X. D. Hawkins*}
    - \author{Michael C. Frank}

affiliation-information:
    # Single affiliation
    - \affiliation{Department of Psychology, Stanford University}

author-note:
    "The Author Note, containing contact information, acknowledgements, etc"

abstract: 
    "Abstract text."

keywords:
    "If provided, keywords will be displayed on a line beneath the abstract."
---

```{r global_options, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
```

@@

# Introduction 
Cite fancy references [@Garnier2007].

# Results 
Results

## Subsection 1 
You can use R chunks directly to plot graphs.

```{r, graph, echo=TRUE, message=FALSE, fig.height=4, fig.width=4, fig.align='center', fig.cap='Figure caption'}
require("ggplot2")
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)
ggplot(data = data.frame(x, y), 
       aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## Subsection 2

# Discussion

# References
